---
title: "univariate and bivariate analysis"
author: "Kahiga Ndegwa"
date: "12/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Loading The dataset

```{r}
advertising <- read.csv("C:/Users/user/Desktop/advertising.csv")
```
##Checking The Data
a.first columns
```{r}
head(advertising)
```
b. last columns
```{r}
tail(advertising)
```
```{r}
nrow(advertising)
```
summary
```{r}
summary(advertising)
```
#Tyding The Dataset
1.looking for duplicates
```{r}
duplicated(advertising)
```
we found that the data had no duplicates
```{r}
colnames(advertising)
names(advertising)[names(advertising) == "Male "] <- "Gender"
```

```{r}
any(is.na(advertising))
```
##EDA
#Univariate Analysis

```{r}
hist(advertising$Age)
```
The average age is 35
```{r}
plot(density(advertising$Age), main="Age Density Spread")
```
```{r}
hist(advertising$Daily.Internet.Usage)
```
```{r}
hist(advertising$Daily.Time.Spent.on.Site)
```
Most people use 70 to 80 hours a day on a site
```{r}
pie(table(advertising$Male), main="male vs female")
```
1 being male And 0 being female
females spend more time than males online

```{r}
pie(table(advertising$Clicked.on.Ad), main="Most likely to click on Ads")
```
1 for Yes and 0 for No



#Bivariate Analysis


```{r}
boxplot(advertising$Daily.Internet.Usage-advertising$Age, notch = TRUE,col=c("grey","gold"), main="Age against internet usage")
```

```{r}
   library(ggplot2)
ggplot(advertising, aes(x = Area.Income, y = Age)) + geom_point()
```

```{r}
sp<-ggplot(advertising, aes(x=Area.Income, y=Daily.Internet.Usage, color=Male)) + geom_point()
sp
```

```{r}
ggplot(advertising, aes(x = Daily.Time.Spent.on.Site, y = Daily.Internet.Usage)) + geom_point()
```
```{r}
mydata <- advertising[, c(1,2,3,4,7,10)]
head(mydata)
#heatmap(mydata)
```

```{r}
cormat <- round(cor(mydata),2)
head(cormat)
```
```{r}
library(reshape2)
melted_cormat <- melt(cormat)
head(melted_cormat)
```

```{r}
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```
high correlation on age & click.on.ads,daily.internet usage&area.income,

#Conclusion

1. Both genders are likely to click on ads equally
2. Bore female spend more time sites compared to males
3. Males use internet more compared to ladies
4. Age bracket of 20 to 30 years are more in area.income


